Untitled

### 2019-07-10 Manuscript_draft/Protest_plot.Rmd
edits

p1<-ggplot(pro_dat_sol,aes(x=traits_sol,y=pro_cor_sol))+
  geom_bar(stat="identity",position="dodge")+theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank())
p2<-ggplot(pro_dat_sol,aes(x=traits_sol,y=sum_squ_sol))+
  geom_bar(stat="identity",position="dodge")+theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank())
p3<-ggplot(pro_dat_sol,aes(x=traits_sol,y=signif_sol))+
  geom_bar(stat="identity",position="dodge")+theme(axis.text.x=element_text(angle=60,hjust=1))

>>>>

p1<-ggplot(pro_dat_sol,aes(x=traits_sol,y=pro_cor_sol))+labs(title="Solanaceae",x="Traits", y = "Correlation")+geom_bar(stat="identity",position="dodge")+theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank())
p2<-ggplot(pro_dat_sol,aes(x=traits_sol,y=sum_squ_sol))+labs(title="",x="", y = "Sum of squares")+
  geom_bar(stat="identity",position="dodge")+theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank())
p3<-ggplot(pro_dat_sol,aes(x=traits_sol,y=signif_sol))+labs(title="",x="", y = "Sum of squares")+
  geom_bar(stat="identity",position="dodge")+theme(axis.text.x=element_text(angle=60,hjust=1))
